---
title: "Analysis of Towed Vehicles the City of Chicago"
author: "Sai Karthik Varanasi"
date: "March 10, 2017"
output: ioslides_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Introduction

The following visual analysis is a visual depiction of the Towed Vehicles data in City of Chicago. This can be used as a pre analysis of finding the make of most towed vehicles and their color and where they have been towed to (Auto Pounds).


**Data**

The data for this can be found at the [City of Chicago's Website](https://data.cityofchicago.org/Transportation/Towed-Vehicles/ygr5-vcbg)
For this analysis I considered the data for the last 4 months (Dec 2016 - Feb 2017) and can be seen in the Data Table Tab of the Graph.

## Graphs Navigation
**Navigating in the Graph**

- Make Analysis
In the Make Analysis, the user has the option of selecting the Type of the Vehicle and the Location of the City to find the distribution of the color of the  cars availabe in the in the respective Auto Pound.

- Location Analysis
The Location Analysis shows the distribution of different vehicles in the Auto Pound for the 4 different Autopounds of City of Chicago.

- Auto Pounds Aggregate
In the Auto Pounds Aggregate, the number of vehicles in the each pound are aggregated in to a histogram.

- Data Table
This has all the data that is used for the analysis.


##Code

The whole code can be found in the Github Repo here. [Github Link](https://github.com/vvrsk/Data-Science-using-R/tree/master/Analysis%20of%20Towed%20Vehicles%20in%20Chicago) 


##Plot


```{r echo = FALSE,message=FALSE,warning=FALSE}
library(readr)
towed_vehicles <- read_csv("./data/Towed_Vehicles.csv", 
    col_types = cols(Model = col_skip(), 
        Plate = col_skip(), State = col_skip(), 
        Style = col_skip(), `Tow Facility Phone` = col_skip()))

library(shiny)
library(plotly)

make <- unique(sort(towed_vehicles$Make))
color<- unique(sort(towed_vehicles$Color))
tow_to <-unique(sort(towed_vehicles$`Towed to Address`))

shinyApp(

ui = fluidPage( 
        mainPanel(
                
                tabsetPanel(
                tabPanel("Summmary",htmlOutput("summary")),
                tabPanel("Make analysis",h3(textOutput("add")),
                            selectInput("type", "Select Type of vehicle", choices = make, selected="ACUR"),
                            selectInput("color", "Select color code", choices = tow_to, selected="10300 S. Doty"),
                            plotlyOutput('myChart',height = "400px")
                         ),
                tabPanel("Location Analysis",plotlyOutput('location_chart',height = "400px")),
                tabPanel("Auto Pounds Aggregate",plotlyOutput('location_chart_aggr',height = "400px")),
                tabPanel("Data Table", dataTableOutput("table"))
        ))
),


server = function(input, output) {  
                
               dataset <- reactive({df<- (towed_vehicles[towed_vehicles$Make == input$type & towed_vehicles$`Towed to Address` == input$color, ])})
                output$add <- renderText({paste("Make of Car is:", input$type)})
                #output$Controls <- renderUI({list(selectInput("type", "Select Type of vehicle", make, selected=name[1]),
                #                                 selectInput("color", "Select color code", color, selected=name[2])
                #                                )
                #        })
             
        output$myChart <- renderPlotly({
                
                p <- plot_ly(dataset(), x = ~Make, type = "histogram", color = ~Color)
                
        }) 
        output$location_chart <- renderPlotly({
                
                p <- plot_ly(towed_vehicles, x = ~`Towed to Address`, type = "histogram", color = ~Make)
                
        })
        
        output$location_chart_aggr <- renderPlotly({
                
                p <- plot_ly(towed_vehicles, x = ~`Towed to Address`, type = "histogram",  text = ~paste('Make of Cars: ', Make))
                
        })
        
        output$table <- renderDataTable(towed_vehicles)
        
        
        txt <- "<br/> <font size='4'>Hello, Thanks for Coming here!! <br/> </font size>
                <ul>
                <li>This is an analyis of how Towed Vechicles are stacked in the 4 different Auto Pounds of <b>City of Chicago</b>. </li>
                <li>For this analysis I considered the data for the last 4 months (Dec 2016 - Feb 2017) and can be seen in the <b>Data Table</b> Tab of the Graph.</li> 
                <li>The <b>Make Anlaysis</b> gives the distribution of cars based on their Make and Color across these Auto Pounds.</li>
                <li>The <b>Auto Pounds Aggregate</b> gives the Aggrate analysis of Auto ponds and the <b>Location Analysis</b> gives the distribution of different vechicles available in each Auto Pound.</li>
                </ul>"
        
        output$summary <- renderUI({ 
               HTML(paste(txt))
        })
        
        
                },
options = list(height = 1100, width = 1100)


)





```




